\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-06-15 paper.qmd
Added best and bad layouts

Projections of the $7\text{-}D$ S-curve data (purple points) overlaid with the model (black grid with  green points indicating bin means) constructed from the UMAP layout, with XXX bins (using the **langevitour** software). The model closely fits the shape of this data. A video of the full tour is available at (<https://youtu.be/G1m4q9k--v4>).
:::

@@

<!--langevitour with best pD model for S-curve-->
::: {#fig-scurve-sc-best layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_best_1.png)

![](figures/scurve/sc_best_2.png)

![](figures/scurve/sc_best_3.png)

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>). MSE with $0.035$.
:::

<!--langevitour with bad pD model for S-curve-->
::: {#fig-scurve-sc-bad layout-ncol="3" fig-pos="H"}
![](figures/scurve/sc_bad_1.png)

![](figures/scurve/sc_bad_2.png)

![](figures/scurve/sc_bad_3.png)

Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/DHPvhkZ0lUM>). MSE with $0.090$.
:::

>>>>

Projections of the $7\text{-}D$ S-curve data (purple points) overlaid with the model (black grid with green points indicating bin means) constructed from the UMAP layout, with 60 non-empty bins (using the **langevitour** software). The model closely fits the shape of this data. A video of the full tour is available at (<https://youtu.be/G1m4q9k--v4>).
:::

@@

<!--langevitour with best pD model for S-curve--> 
<!-- ::: {#fig-scurve-sc-best layout-ncol="3" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_best_1.png) -->

<!-- ![](figures/scurve/sc_best_2.png) -->

<!-- ![](figures/scurve/sc_best_3.png) -->

<!-- Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/4RFNENX_fXk>). MSE with $0.035$. -->
<!-- ::: -->

<!--langevitour with bad pD model for S-curve--> 
<!-- ::: {#fig-scurve-sc-bad layout-ncol="3" fig-pos="H"} -->
<!-- ![](figures/scurve/sc_bad_1.png) -->

<!-- ![](figures/scurve/sc_bad_2.png) -->

<!-- ![](figures/scurve/sc_bad_3.png) -->

<!-- Screen shots of the **langevitour** of the S-curve, shows the model-in-data space, a video of the tour animation is available at (<https://youtu.be/DHPvhkZ0lUM>). MSE with $0.090$. -->
<!-- ::: -->

### 2024-06-15 paper.tex
Added best and bad layouts

\caption{\label{fig-scurve-sc}Projections of the \(7\text{-}D\) S-curve
data (purple points) overlaid with the model (black grid with green
points indicating bin means) constructed from the UMAP layout, with XXX
bins (using the \textbf{langevitour} software). The model closely fits
the shape of this data. A video of the full tour is available at
(\url{https://youtu.be/G1m4q9k--v4}).}

@@

In contrast, a poor model for the S-curve with UMAP was created using
only \(190\) bins and removing edges with a length greater than \(0.3\).
This model is inadequate as it has a higher MSE compared to the
appropriate model. Visually, the model does not fit the points in some
places and mismatches the pattern (Figure~\ref{fig-scurve-sc-bad}).

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_best_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc-best}Screen shots of the
\textbf{langevitour} of the S-curve, shows the model-in-data space, a
video of the tour animation is available at
(\url{https://youtu.be/4RFNENX_fXk}). MSE with \(0.035\).}

\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_1.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_2.png}\end{minipage}%
%
\begin{minipage}{0.33\linewidth}
\includegraphics{figures/scurve/sc_bad_3.png}\end{minipage}%

\caption{\label{fig-scurve-sc-bad}Screen shots of the
\textbf{langevitour} of the S-curve, shows the model-in-data space, a
video of the tour animation is available at
(\url{https://youtu.be/DHPvhkZ0lUM}). MSE with \(0.090\).}

>>>>

\caption{\label{fig-scurve-sc}Projections of the \(7\text{-}D\) S-curve
data (purple points) overlaid with the model (black grid with green
points indicating bin means) constructed from the UMAP layout, with 60
non-empty bins (using the \textbf{langevitour} software). The model
closely fits the shape of this data. A video of the full tour is
available at (\url{https://youtu.be/G1m4q9k--v4}).}

@@

In contrast, a poor model for the S-curve with UMAP was created using
only \(190\) bins and removing edges with a length greater than \(0.3\).
This model is inadequate as it has a higher MSE compared to the
appropriate model. Visually, the model does not fit the points in some
places and mismatches the pattern (\textbf{?@fig-scurve-sc-bad}).
